---
title: "Homework8"
author: "Jonathan Pilling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

Here we test some hypotheses about cardiac measurements.
You want to test the hypothesis that men are more likely to have hypertension than women.
Hypertension is the variable hxofHT (be careful, hxofHT = 0 indicates they do have hypertension)
and gender is male = 0, female = 1. Use the Fisher exact test to get a p value for
this hypothesis test. Can you reject the null hypothesis at the ?? = 0.05 level?

__Answer:__

```{r}
cardiac = read.csv("cardiac.txt")
tab = table(cardiac$hxofHT, cardiac$gender) #Create the contigency table
fisher.test(tab, conf.int=T, conf.level = 0.95)
```
Because in our fisher test the p value is less than 0.05, the Null hypothesis is rejected.

## Problem 2

## Problem 3

## Problem 4

Write an R function my.regression(x, y) that computes the regression of an independent
variable x and a dependent variable y. It should return the estimated slope and intercept.
```{r}
my.regression <- function(x, y){
  #This function will take in an x and a y value, and return the estimated slope and intercept
  
  b = cor(x,y) * (sd(y)/sd(x)) #Slope of regression line
  
  a = mean(y) - b * mean(x) #y intercept of regression line
  
  return(list(a = a, b = b))
}
```
__(a)__

Run your regression command on the faithful data

__Answer:__

```{r}
waiting = faithful$waiting
eruptions = faithful$eruptions

regression_line <- my.regression(waiting, eruptions)
my.regression(waiting, eruptions) # This repeat is to show the slope and intercept

plot(waiting, eruptions, main = "Eruption vs. Waiting Time : my.regression function")
abline(regression_line$a, regression_line$b, col= "red", lwd = 3)
```

__(b)__

From regression model info: $-1.87 + 0.075 * 82 = 4.28$

Estimated at 4.28 min

__(c)__

```{r}
faithful.model = lm(eruptions ~ waiting, data = faithful)
plot(faithful$eruptions ~ faithful$waiting, main = "Eruptions vs. Waiting Time : lm function")
abline(faithful.model, col = "red", lwd = 3)

```

__(d)__

```{r}
summary(faithful.model)
```

Because the p value is so small, we can reject the null hypothesis and waiting for eruptions is significant based on whether an eruption will happen soon or not.




